---
title: "p8105_hw1_yz5290"
author: "Yue Zhao"
date: "2025-09-20"
output: github_document
---

problem 1:
```{r}
library(moderndive)
library(tidyverse)
```
```{r}
data("early_january_weather")
```

The early_january_weather dataset contains `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. Important variables include:`temp` which is the temperature in Fahrenheit; `humid` which is the relative humidity; `precip` which is the precipitation; `year`, `month`, `day`, and `hour` are the date and time. The mean temperature of early january is `r mean(early_january_weather$temp, na.rm = TRUE)` °F.

scatter plot:
```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid))+
  geom_point(alpha = 0.5)+
  labs(
    x = "Hour",
    y = "Temperature (F)",
    color = "Humidity",
    title = "Temperature vs Time in Early January (NYC)"
  )
```
save the plot
```{r}
ggsave("scatter_plot.pdf", height = 4, width = 6)
```

Problem 2:
```{r}
set.seed(1)#make it reproductable
```
```{r}
my_df= tibble(num = rnorm(10),is_positive = rnorm(10) > 0,chars = sample(letters, 10),factors = factor(rep(c("low", "med", "high"), length.out = 10)))
my_df
```
Take the mean:
```{r}
mean(my_df |> pull(num))          #works
mean(my_df |> pull(is_positive))  #works
mean(my_df |> pull(chars))        # doesn't work
mean(my_df |> pull(factors))      # doesn't work
```

```{r}
as.numeric(my_df |> pull(is_positive))
as.numeric(my_df |> pull(chars))
as.numeric(my_df |> pull(factors))
```

What happened and why:
is_positive convert to numeric 1 and 0. character cannot be converted. factors convert to integral according to its level like "low, median, and high" to "1,2,3". It's because numeric and logical can take the average mean but characters cannot. Factors can convert to numeric but I have to write the code to do so. 






